A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-17 paper.tex
modify figure2,3 and section 5 and 6

The relationship of different roles involved in the experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
responsible for generating one package with the help of the packaging utility. Then the package, together with
its map file and description file will be uploaded into the archive. When
another scholar wants to repeat the experiment, one copy of the package and its
corresponding map file will be downloaded into the new machine.

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        \bf Archive Path & \bf Service Description \\ \hline
        {\tt /archive/OS/path} & OS Image \\ \hline
        {\tt /archive/software/path} & Common Software Library \\ \hline
        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
        {\tt /archive/git/path} & Git Software Library \\ \hline
        {\tt /archive/http/path} & HTTP resources \\ \hline
        {\tt /archive/experiment/path} & experiment private files \\ \hline
        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
    \end{tabular}
    \caption{Structure Organization of the Archive}
    \label{table:archive-map}
\end{table}

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
Item {\tt /archive/OS} includes the images of different Operating Systems.
Item {\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
archive, each sub-item should include the private files and description files of each experiment.

One map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file on the client side.

The archive supports two different data preservation models: Internal and External. Internal method will preserve the data in the archive. External method refuses to preserve the content of data, but only preserve the reference to the actual storage place of data. For example, the size of experiment data from the Grid is extremely large, and storing the same data in the archive is time-consuming and space-consuming. Through External method, the archive only preserves one reference to the data inside the remote Grid.

This solution tries to create one self-contained and independent package for
each experiment and integrate different packages for different experiments into
one archive to multiplex common data. One packaging utility, which can figure out all the really used data of one program  will be provided
to help the original author to generate the package. The archive can maintain
the experiment dependencies through Internal or External method. The archive
itself will be responsible for the data maintenance and relevant authority
access problem. The new user can repeat one experiment through the
interaction with the archive.

@@

The toolkit iterates each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing all the necessray file dependnencies, and returns the description
information of the package, as shown in Table~\ref{table:package-info}.  To
ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may only
access the metadata of one file with the size of 200GB.  Our solution is to
determine the replication degree of one directory or one file according to the
system call type. The step also runs under Parrot to access data from
different file systems.

@@

When another scholar wants to repeat the analysis program,
one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
, will be generated, as shown in Table~\ref{table:map-file}.
The path of the package is {\tt /tmp/package-hep}, so the actual location of one file with the original path {\tt path1} will be {\tt /tmp/package-hep/path1}.
However, 
it is impossible to copy the files under certain directories, such as  {\tt /dev}, which can halt the packaging process.
It is meaningless to copy the file under the directory {\tt /proc}, because the process id of one program is random and depends on the
current allocation of process ID.
As for these special file paths, letting
the program directly utilize the files on the new machine, where the new user
repeats the program, is a better choice. 
The item {\tt /dev /dev} of Table~\ref{table:map-file}
illustrates this semantics.
With the help of the map file and the package, the application can be repeated on one new machine.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Actual Analysis & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

Table~\ref{table:time-3rd} illustrates the time used to
obtain the filename list and generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the experiment
separately.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    \bf Sub-Task &\bf Time \\ \hline
    Obtain filename list & 28min 23s \\ \hline
    Generate package & 85min 51s \\ \hline
    \end{tabular}
    \caption{Time Used to Obtain Filename List and Generate Package}
    \label{table:time-3rd}
\end{table}

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the curation environment that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A reearcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

>>>>

The relationship of different roles involved in the experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
Then the package, together with
its map file and description file will be published. When
another researcher wants to repeat the experiment, one copy of the package will be downloaded into the new machine and the application can be repeated.

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

@@

The toolkit iterates each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing all the necessary file dependencies, and returns the description
information of the package, as shown in Table~\ref{table:package-info}.  To
ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may 
only need to know how many items one directory contains and not need the content of the sub-dirctories or the sub-files.
Our solution is to
determine the replication degree of one directory or one file according to the
system call type. 
If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
As for a directory item, the sub-items under it will be copied into the package if their contents are necessary. Otherwise, we only create empty sub-items in the package to maintain the directory structure.
The step also runs under Parrot to access data from
different file systems.

@@

When another researcher wants to repeat the analysis program,
one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
, will be generated, as shown in Table~\ref{table:map-file}.
The path of the package is {\tt /tmp/package-hep}, so the actual location of one file with the original path {\tt path1} will be {\tt /tmp/package-hep/path1}.
However, 
it is impossible to copy the files under certain directories, such as  {\tt /dev}, which contains all the device files.
Each device file is either a block file or a character file. 
The new machine may not share the same device configuration with the original machine, so copying block files into the package is meaningless.
Copying character files such as /dev/tty and /dev/urandom is also meaningless because of their dynamic nature.
It is meaningless to copy the file under the directory {\tt /proc}, 
because OS may allocate different process IDs for multiple executions of one application.
As for these special file paths, letting
the program directly utilize the files on the new machine, where the new user
repeats the program, is a better choice. 
The item {\tt /dev /dev} of Table~\ref{table:map-file}
illustrates this semantics.
With the help of the map file and the package, the application can be repeated on one new machine.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Obtain filename list & N/A & 28min 23s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Actual Analysis & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

Table~\ref{table:time-2nd3rd} also illustrates the time used to
obtain the filename list and generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the experiment
separately.

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A reearcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.
